$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-19 paper/e6ssm-tuning-paper.tex
changed footnote to emphasise agreeemnt when trace vanishes.
remove duplicated the in several places.

Nonetheless the MSSM the impact of potential chargino mass limits is
shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the the
full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded the
impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
slightly worse than that of the E$_6$SSM with the same cutoff and a
$Z^\prime$ mass just larger than current limits. In the E$_6$SSM,
while raising the chargino limit can have the same impact in
principle, due to current limits on the $Z^\prime$ mass already
imposing a significant degree of tuning, chargino masses do not make
much of a noticeable change.

@@

Prior to stringent experimental constraints on the mass of the
lightest Higgs boson and squarks in supersymmetric models, a simple
picture of a natural SUSY model emerged from theoretical reasoning,
with soft masses set to similar values at the GUT scale through local
gravity interactions with the hidden sector.  Through the use of
renormalisation group running one can then see that at the EW scale
the stops and soft Higgs masses (which appear directly in the EWSB
conditions) should appear in the the EWSB condition for $M_Z$ and
therefore it was expected that these masses should not be much bigger
than $100$ GeV.  However to disturb this elegant picture first LEP
placed constraints on the Higgs mass, requiring it to be above 114.4
GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced significant tuning for
constrained models, since heavy stops are required to raised the
lightest Higgs mass above it's tree level bound. Recently this problem
got much worse since the LHC measured the Higgs to be around $125$
GeV.

@@

  \cite{Martin:1993zk}.  Although we use the the NoU1Mixing to neglect

@@

  \cite{Martin:1993zk} nor those which appear in \cite{Athron:2009bs}.
  Note however these contributions do not appear in the

>>>>

Nonetheless the MSSM the impact of potential chargino mass limits is
shown in Fig.~\ref{Fig:chargino-plot}.  There we see that if the 
full parameter space with $m_{\tilde{\chi}^\pm_1} < 700$ GeV was excluded the
impact would be to make the tuning in the MSSM with a $20$ TeV cutoff
slightly worse than that of the E$_6$SSM with the same cutoff and a
$Z^\prime$ mass just larger than current limits. In the E$_6$SSM,
while raising the chargino limit can have the same impact in
principle, due to current limits on the $Z^\prime$ mass already
imposing a significant degree of tuning, chargino masses do not make
much of a noticeable change.

@@

Prior to stringent experimental constraints on the mass of the
lightest Higgs boson and squarks in supersymmetric models, a simple
picture of a natural SUSY model emerged from theoretical reasoning,
with soft masses set to similar values at the GUT scale through local
gravity interactions with the hidden sector.  Through the use of
renormalisation group running one can then see that at the EW scale
the stops and soft Higgs masses (which appear directly in the EWSB
conditions) should appear in the EWSB condition for $M_Z$ and
therefore it was expected that these masses should not be much bigger
than $100$ GeV.  However to disturb this elegant picture first LEP
placed constraints on the Higgs mass, requiring it to be above 114.4
GeV \cite{Barate:2003sz,Schael:2006cr}, which already introduced significant tuning for
constrained models, since heavy stops are required to raised the
lightest Higgs mass above it's tree level bound. Recently this problem
got much worse since the LHC measured the Higgs to be around $125$
GeV.

@@

  \cite{Martin:1993zk}.  Although we use the NoU1Mixing to neglect

@@

  \cite{Martin:1993zk} or \cite{Athron:2009bs} unless $\Sigma_{Q}^Y =
  0$.  Note however these contributions do not appear in the
